\makeheading{Ericson Cepeda}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\begin{minipage}[t]{\textwidth-\rcollength-0.5cm}
Rinc\'{o}n de Santa Ana\newline
Cra 7 Este \# 25 - 59\newline
Ch\'{i}a, Cundinamarca Colombia
\end{minipage}
\begin{minipage}[t]{\rcollength-0.5cm}
\colorbox{shade}{\textcolor{text1}{
% \begin{tikzpicture}[overlay, opacity=0.8, color=black, xshift=0.3cm,
% yshift=-40pt] \draw node {\slash 2.\slashAlt 0};%
% \end{tikzpicture}
\begin{tabular}[t]{c|l@{}}%
%\href{http://sistemas.uniandes.edu.co/}%
%     {Departamento de Ingeniería de Sistemas y Computación} & \\
%\href{http://www.uniandes.edu.co/}{Universidad de los Andes}
\raisebox{-3pt}{\PhoneHandset} 
& $(300) 557-4311$ \\
\raisebox{-3pt}{\Phone} 
& $+57(1) 870-8806$ \\
\raisebox{-3pt}{\Envelope}
& 
\href{mailto:e-cepeda@uniandes.edu.co}{e-cepeda@uniandes.edu.co}\\
% &	\icons{http://twitter.com/ericsonlopez} {twitter.png}  
% 	\icons{http://delicious.com/} 		{rss.png}
% 	\icons{http://www.facebook.com/ericson.lopez} 	{facebook.png}
% 	\icons{http://www.flickr.com/} 		{rss.png} 
% 	\icons{http://www.last.fm/} 			{rss.png} 
% 	\icons{http://www.vimeo.com/} 		{rss.png} 
% 	\icons{http://www.stumbleupon.com/} 	{rss.png}
% 	\icons{http://www.reddit.com/} 		{rss.png} 
% 	\icons{http://www.linkedin.com/}		{linked.png} 
\end{tabular}
}}%
\end{minipage}


\section{Profile}
%
Undergraduate student of Computing and Systems Engineering, highly motivated,
and in capacity of developing software applications on different platforms, implementing different stages in group or individually. Besides, recognising the business processes involved in the implementation of a solution. This is complemented with a wide knowledge of different operative systems.

%\section{Security Clearance}
%
%Department of Defense Top Secret SCI with polygraph (expired: 2002)

% \section{Citizenship}
%
% Colombia

\section{Education}
%
% \href{http://idic.edu.co/}{\textbf{IDIC}},
% Bogot\'{a}, Colombia
% \begin{outerlist}
% \item[] Grades: Kindergarten - $11$th \hfill \textbf{1992 - 2004}
% \end{outerlist}
% 
% \halfblankline 
% 
\href{http://www.uniandes.edu.co/}{\textbf{Universidad de los Andes}},
Bogot\'{a}, Colombia
\begin{outerlist}
\item[] Computing and Systems Engineering \hfill \textbf{2005 - Present}
    \begin{innerlist}
    	\item GPA: $3.5$
    \end{innerlist}
\end{outerlist}

\section{Professional Experience}
%
\href{http://convertimedia.com/}{\textbf{Converti Media}}, Bogot\'a, Colombia.
Consultancy and online communication strategies development enterprise,
specialized on digital media.
\begin{outerlist}
\item[] Junior web developer \hfill \textbf{November 2010 - May 2011}
    \begin{innerlist}
    	\item Engineered implementations to bring the
    	WHMCS functionalities, from the account held by the company, into a
    	brand new Wordpress site.
		\item Data mining (MySQL), Wordpress developing and WHMCS management for
		domain reselling.
		\item PHP and Javascript (jQuery) programming for specified web services.
    \end{innerlist}
\end{outerlist}

\halfblankline 

\href{http://irradiadiseno.com/}{\textbf{Irradia Dise\~no}}, Bogot\'a, Colombia.
Young designers group with an effective and creative approach for the needs of
SMEs in Colombia.
\begin{outerlist}
\item[] Web developer (freelance) \hfill \textbf{June 2011 - July 2011}
    \begin{innerlist}
\item Researched and redesigned the core functionalities of
\href{http://www.alacartagourmet.com/}{\textbf{A La Carta}}, in such
way it would behave as required, making 100\% of the clients able to order
online.
\item PHP (Joomla) y Javascript (jQuery) programming of required web pages.
\item MySQL DBMS management to meet new requirements.
    \end{innerlist}
\end{outerlist}

\halfblankline 

\href{http://www.sukhaweb.com/}{\textbf{Sukha SAS.}}, Bogot\'a, Colombia.
Multipurpose company that integrates:
international product trading, software development, home-automation and organic
products fair-trading.
\begin{outerlist}
\item[] IT manager \hfill \textbf{February 2011 - Present}
    \begin{innerlist}
\item Built the company main website, seeking for creative, minimalistic and
attractive ways to show the company profile. Manage the company web infrastructure with the
aim of economic, but optimal solutions.
\item PHP (CakePHP) and Javascript (jQuery) programming for the website.
\item MySQL DBMS administration.
    \end{innerlist}
\end{outerlist}

\halfblankline 

\href{http://www.piedradigital.com/}{\textbf{Piedra Digital}}, Bogot\'a,
Colombia. Consultancy and software development company, which gives balance
between strategic solutions and their implementation.
\begin{outerlist}
\item[] Systems analyst and developer \hfill \textbf{March 2011 - June 2012}
    \begin{innerlist}
\item Accomplished the production and release of
two projects, Aurora (CakePHP) and
\href{http://demo.100grados.co:8080/desempeno100/}{\textbf{Mediros2}} (Grails), together with a rapid development team.
\item Java (core, Grails) and Javascript (jQuery) based programming.
\item Data mining with SQL Server and PostgreSQL.
    \end{innerlist}
\end{outerlist}

\halfblankline 

\href{http://sqbluesky.com/}{\textbf{SQBlueSky Inc.}}, Dallas, TX USA. Small
niche financial company focused on building and offering useful investment research tools.
\begin{outerlist}
\item[] Systems analyst and developer \hfill \textbf{May 2012 - Present}
    \begin{innerlist}
\item Guided the integration between the current
\href{http://app.insideredge.com/}{\textbf{Insider Edge}}
website and the new CouchDB implementation, for a faster and more reliable service.
\item PHP (Zend Framework) and Javascript (jQuery) based programming.
\item Data mining with CouchDB and MySQL.
    \end{innerlist}
\end{outerlist}

% \blankline




% \pagebreak 

\section{Portfolio}
%
Projects:
\begin{innerlist}
\item \href{http://www.alacartagourmet.com/}{\textbf{A La Carta}}
\item \href{http://www.sukhaweb.com/}{\textbf{Sukha SAS}}
\item \href{http://demo.100grados.co:8080/desempeno100/}{\textbf{Mediros2}}
\item \href{http://app.insideredge.com/}{\textbf{Insider Edge}}
\end{innerlist}
% 
% \begin{innerlist}
% \item[] \thumbnail	{http://www.voiceoverplace.com/}{mediros.png}
% 		\thumbnail	{http://www.alacartagourmet.com/final/}{carta.jpg}
% 		\thumbnail	{http://www.sukhaweb.com/}{sukha}
% 		\thumbnail	{http://www.sukhaweb.com/}{insider.png}
% \end{innerlist}

\section{Technical Skills}
%
% Hardware and software experience in networking, and information technology
% 
% \halfblankline
% 
Computer programming: 

    \begin{innerlist}
\item Advanced: Core Java 
\item Intermediate: Groovy (Grails), JavaScript (jQuery), PHP (CakePHP, Zend,
Wordpress, Joomla), SQL (MySQL, PostgreSQL, SQL Server), \LaTeX{},  Java (JUnit, JSF, Servlet, JSP,
J2EE)
\item Apprentice: C, C$+$$+$, Express-MP, Matlab, VHDL, CouchDB, Python (UNIX
shell scripting)
\item Beginner: Objective C
    \end{innerlist}

\halfblankline

Information technology: 
    \begin{innerlist}
\item Networking (UDP, TCP, ARP, DNS, Dynamic
        routing)
\item Service (Apache, Wiki, Wamp Server, phpMyAdmin,
        cPanel)
    \end{innerlist}

\halfblankline

Computer applications: 
    \begin{innerlist}
\item Eclipse, SSH Secure Shell, BiZZdesign
Architect, Adobe: Illustrator, Flash Catalyst, Flash Builder, Dreamweaver, and others
\item Most common productivity packages (for Windows, and Linux platforms)
    \end{innerlist}

\halfblankline

Computer-aided design: 
    \begin{innerlist}
\item Xilinx, SPICE
    \end{innerlist}


\halfblankline

Operative systems: 
    \begin{innerlist}
\item Microsoft Windows family  
\item Ubuntu, and other UNIX variants
    \end{innerlist}


\section{Languages}
%
Spanish: Native. English: Advanced

\halfblankline

English: IELTS: 6.0 (December 2009) Reading: Excellent. Writing: Very good. Listening and speaking: Good

\halfblankline

International House Bristol (The Language Project), Bristol, UK - Curso: General English 20, 1st February - 7th May, 2010

\section{Interests and Achivements}
%
\textbf{Individual}
\begin{outerlist}
% \item[] Agent-based modeling, hybrid systems, distributed algorithms, cloud computing, artificial intelligence%
\item[] It has grown a sense of humanity and social
responsibilitiy  through some meditation experiences. One of the main
goals is helping people with unconditional love, and the world to be a better
place to live in. There are few places where one can meet the needed aim and
expertise to achieve those objectives from technology side. That is why there is
an impulse to be technologically green.
\end{outerlist}

\halfblankline

% \textbf{Non-academic activities}
% 
% \begin{outerlist}
% 
% \item[] I frequently practise sports, such as basketball or swimming. Altough, I spend some time searching information about science advances and technology, as well as, improving my intellect doing some reading on literature, or being autodidact with some informatics thematics%
% \end{outerlist}
% 
% \blankline

\textbf{Reading course}
\begin{outerlist}

\item[] \href{http://www.tecnicasamericanas.com/}{T\'ecnicas Americanas
de Estudio}, Bogot\'a, Colombia%
        \\ \textbf{January - May 2005}
\begin{innerlist}
\item Reading comprenhension and speed improving.
\end{innerlist}
\end{outerlist}

\halfblankline

\textbf{Voluntary service}
\begin{outerlist}

\item[] \href{http://www.dipa.dhamma.org/}{Dhamma Dipa Meditation Centre},
Hereford, UK%
        \\ \textbf{25th May - 5th June 2010}
\begin{innerlist}
\item Performed as a member of the kitchen team for 150 Vipassana meditation
students, during 10 days.
\end{innerlist}
\end{outerlist}

\section{References}
%
Available upon request
%\href{mailto:mfonseca@procalculo.com}{\textbf{Mónica Fonseca Puentes}}
%\begin{outerlist}
%
%\item[] Directora Help Desk%
%        \hfill \href{http://www.procalculoprosis.com/}{\textbf{Procalculo Prosis S.A.}}
%\begin{innerlist}
%\item Tel: +57(1) 6501550 Ext.3313    
%\item Cel: (300) 5704573  
%\item Cel: (310) 7534086
%\end{innerlist}
%\end{outerlist}
%
%\blankline
%
%\href{mailto:samafi85@gmail.com}{\textbf{Sandra Madrigal Fierro}}
%\begin{outerlist}
%
%\item[] Ingeniera en ICBF (Servicio al consumidor)%
%        \hfill \href{https://www.icbf.gov.co/}{\textbf{ICBF}}
%\begin{innerlist}
%\item Cel: (316) 636-2777    
%\end{innerlist}
%\end{outerlist}